--- 
title: "Deep Learning with Pytorch: Explained Tutorials"
author: "서용덕 Yongduek Seo yndk@sogang.ac.kr"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "Pytorch practice and deep learning. There are many tutorials in pytorch.org. Explanations are attached to learn it."
---



- MacOS: python 3.7 install `https://docs.python.org/3/using/mac.html`
- MacOS:`matplotlib` backend problem can be solved by 
    - Create a file `~/.matplotlib/matplotlibrc` there and add the following code: `backend: TkAgg`


# Prerequisites


1. Install `pytorch`, `python 3.x`, `anaconda`
1. `numpy` and `torch.Tensor`
1. Simple linear regression 
    - a line fitting for a data set of almost no noise: $y = w x + b$
    - random number generation for training and test
1. Simple two class classification
    - random number generation: uniform and Gaussian
    - feature and label - random data generation
    
1. Simple linear regression & classification with `DataLoader` & `DataSet`
    - Using `torch.nn` for the two simple problems: 
    - `class myNetwork(torch.nn)`
    - `optim` package
    
1. Sobel Operater Learning with Convolutional Neural Network
    - Single data example
    - Sobel ?
    - convoltuion ?
    - single channel (gray scale) and multi-channel (RGB)
    
1. MNIST image classification
    1. With Fully connected network
        - `numpy.ravel()`
    1. With Convolutional Neural Network

1. Dogs and Cats with Transfer Learning
    - ResNet, DensetNet, VggNet, etc
    - Transfer Learning: Use a trained network for classification of not-trained sources.
    
1. Dogs Breed Classification
    - Kaggle interface
    - Transfer Learning
  
1. Direct Font Style Transfer
    - Using `PIL` to draw characters on the image bitmap
    - `numpy` as image data container



This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

Python 언어를 사용하는 방법은 ... 쉽다.

```{bash}
which python3
```

<!--  Mac OS X -->
``` {r}
knitr::opts_chunk$set(engine.path = list(
  #python = '/Library/Frameworks/Python.framework/Versions/3.7/bin/python3'
  python='/usr/local/bin/python3'
))
```

```{python}
import sys
print (sys.version)
```

